---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chromodoris

<!-- badges: start -->
<!-- badges: end -->

chromodoris is an R package in development for one plot type, the
Chromodoris plot. A Chromodoris plot takes many time series, one per
participant or unit, and summarizes them moment by moment as nested quantile
ribbons (for example the inner 90%, 70%, and 50% of values) around a center
line, in place of a spaghetti plot of overlaid series.

The package is a ggplot2 extension with two layers. `stat_chromodoris()`
computes the bands from long data (columns for series id, time, and value)
inside any ggplot pipeline. `chromodoris()` draws the whole plot with
default scales and theme.

## Installation

The package is not on CRAN. Once the GitHub repository is public, you can
install the development version with:

``` r
# install.packages("pak")
pak::pak("jmgirard/chromodoris")
```

## Usage

```{r example, fig.width = 7, fig.height = 4, dpi = 120}
library(chromodoris)
set.seed(1)
# 20 raters sampled 10 times per second over 40 seconds: a shared signal,
# a per-rater offset, and slowly drifting per-rater noise.
time <- seq(0, 40, by = 0.1)
d <- expand.grid(time = time, id = 1:20)
d$value <- sin(d$time / 6) +
  rnorm(20, sd = 0.3)[d$id] +
  ave(rnorm(nrow(d), sd = 0.06), d$id,
      FUN = function(e) stats::filter(e, 0.985, method = "recursive"))
chromodoris(d, id, time, value)
```

Ratings sampled faster than they change give jagged bands: with 20 raters,
each edge of the 90% band follows one rater's value at every one of the
401 time points, so it jumps whenever that rater moves.
`bin = 0.5` averages each rater within 0.5-second bins (2 Hz, so 81 bins
across the 40 seconds, the last holding only the sample at 40 s) before
the bands are computed. `bin_series()` does
the same binning on a data frame.

```{r binned, fig.width = 7, fig.height = 4, dpi = 120}
chromodoris(d, id, time, value, bin = 0.5)
```
