---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chromodoris

<!-- badges: start -->
<!-- badges: end -->

chromodoris is an R package in development for one plot type, the
Chromodoris plot. A Chromodoris plot takes many time series, one per
participant or unit, and summarizes them moment by moment as nested quantile
ribbons (for example the inner 90%, 70%, and 50% of values) around a center
line, in place of a spaghetti plot of overlaid series.

The package is a ggplot2 extension with two layers. `stat_chromodoris()`
computes the bands from long data (columns for series id, time, and value)
inside any ggplot pipeline. `chromodoris()` draws the whole plot with
default scales and theme.

## Installation

The package is not on CRAN. Once the GitHub repository is public, you can
install the development version with:

``` r
# install.packages("pak")
pak::pak("jmgirard/chromodoris")
```

## Usage

```{r example, fig.width = 7, fig.height = 4, dpi = 120}
library(chromodoris)
set.seed(1)
d <- expand.grid(id = 1:20, time = 1:40)
d$value <- sin(d$time / 6) + rnorm(nrow(d), sd = 0.5)
chromodoris(d, id, time, value)
```
